Diversification of salmon fishermen within strategies (permits)

### 2016-08-11 salmon/analysis/salmon_paper.Rmd
suppress warnings / add residuals

```{r, echo = FALSE}
pdf("Salmon_residuals.pdf")
# Residuals for mean model
dat.salmon$mu.resid = residuals(mu.mod)
dat.salmon$mu.fitted = fitted(mu.mod)

>>>>

```{r, echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
pdf("../../salmon/Salmon_residuals.pdf")
# Residuals for mean model
dat.salmon$mu.resid = residuals(mu.mod)
dat.salmon$mu.fitted = fitted(mu.mod)
